Digital History in Finland, 1488-1828

### 2017-02-01 inst/examples/manuscript-krakow.Rmd
manuscript figs

```{r linkoping3, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=5}
dfs <- df %>% select(publication_year, publisher) %>%
	      filter(!is.na(publisher)) %>%
              unique %>%	      
	      arrange(publication_year) 
kable(dfs)
.```

>>>>

```{r linkoping3, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=5}
dfs <- df %>% select(publication_year, publisher) %>%
	      filter(!is.na(publisher)) %>%
              unique %>%	      
	      arrange(publication_year) 
kable(dfs)
```
